Measuring Political Freedom Around the World

### 2020-11-12 slides.Rmd
worked on slides

* What factors are associated with an increase in political freedom?

@@

* covarites w/ exp

@@

# Summary Stats

>>>>

* This study will focus on political freedom around the world.

* We ask: What factors are associated with an increase in political freedom?

@@

# Covariates

- Country

- Year from 2000 to 2018

- Corruption Perception Index Ranging from 0 to 100 with 0 being the most corruption perception.

- Education Expenditure in GDP per Person

- Electricity use per person in Kilowatt Hours.

- Gini Coefficient. A measure of a nation's wealth inequality ranging from 0 being perfectly equal distribution of income and 1 being one person has all nation's wealth.

- Percentage of population That use the Internet.

- Labor Force Participation.

- Life Expectancy

- Military Spending as a percentage of GDP

- Murders per million people.

@@

```{r message=FALSE}
data %>% 
  group_by(country) %>% 
summarise(across(.cols = c(corruption_perception_index_cpi:murder_per_mil_people), mean)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  kable(
    col.names = c("Country", "CPI", "Edu Exp", "Electric Use", "Gini", "Internet Users", "Labor Force", "Life Expectancy","Military Spending", "Murder Rate")) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 6, fixed_thead = T)
```

```{r}
data %>% 
  group_by(polrights_fh) %>% 
  add_count(polrights_fh) %>% 
  ggplot() + 
  geom_bar(aes(x = polrights_fh)) + 
  geom_text(aes(x = polrights_fh, y = n, label = n)) + 
  scale_x_continuous(breaks = 1:7) + 
  theme_test()
```
